---
title: DATA 606 Data Project Proposal
author: Sung Lee
---

### Data Preparation

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
# load data
library(tidyverse)
library(psych)
library(summarytools)
library(ggplot2)

licenses_df <- read_csv("https://raw.githubusercontent.com/logicalschema/Data606Project/master/License_Applications.csv.gz")

names(licenses_df)<-str_replace_all(names(licenses_df), c(" " = "_"))

head(licenses_df)

names(licenses_df)

```




### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**

Do economic downturns impact the number of tobacco and liquor license applications in NYC?


### Cases 

**What are the cases, and how many are there?**

There are 368,017 applications and renewals for NYC business licenses in varying license categories from 4/10/98 to 4/16/20. 


### Data collection 

**Describe the method of data collection.**

Data is collected by NYC and recorded on their OpenData platform: https://data.cityofnewyork.us/. This is the original page of the data: https://data.cityofnewyork.us/Business/License-Applications/ptev-4hud/data


### Type of study 

**What type of study is this (observational/experiment)?**

This is an observational study.

### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**

This is the link for the data: https://data.cityofnewyork.us/Business/License-Applications/ptev-4hud

Additional information about the data: https://data.cityofnewyork.us/api/views/ptev-4hud/files/e9ee6ec0-796d-4273-853f-0ccd05920c2f?download=true&filename=DCA%20License%20Applications%20Data%20Dictionary.pdf 


### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**

The response variable is the *License Category* and it is qualitative.


### Independent Variable

**You should have two independent variables, one quantitative and one qualitative.**

The two independent variables are: *Start Date* (quantitative) and *Application or Renewal* (qualitative).

### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

```{r}
dfSummary(licenses_df$License_Category)
dfSummary(licenses_df$Start_Date)
dfSummary(licenses_df$Application_or_Renewal)


tobacco <- filter(licenses_df, License_Category == "Tobacco Retail Dealer")


formatDate <- strptime(as.character(tobacco$Start_Date),format="%m/%d/%Y")
hist(formatDate,breaks=10,xlab="year")


```

